\mytitle

### 2021-12-07 paper.tex
use widetext for longish equations
improve text

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[german]{authblk}
\usepackage[format=plain,labelfont={bf}]{caption}
\usepackage{listings}
\usepackage[shortcuts]{extdash} % \-/
\usepackage{xcolor}
\usepackage{hyperref}

@@

We will define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$
as the real part of the complex continuation of the dilogarithm.  The
real dilogarithm can be mapped onto the interval $[0,1/2)$ by using
the following identities:
%
\begin{align}
  \Li(x) &= -\Li\left(\frac{1}{1-x}\right) - \frac{\pi^2}{6} + \log(1-x)\left[\frac{1}{2}\log(1-x) - \log(-x)\right], \quad (x<-1), \\
  \Li(x) &= -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\log^2(x), \quad (-1<x<0), \\
  \Li(x) &= -\Li(1-x) + \frac{\pi^2}{6} - \log(x) \log(1-x), \quad (\frac{1}{2}\leq x<1), \\
  \Li(x) &= \Li\left(1-\frac{1}{x}\right) + \frac{\pi^2}{6} - \log(x)\left[\log\left(1-\frac{1}{x}\right) + \frac{1}{2}\log(x)\right], \quad (1<x<2), \\
  \Li(x) &= -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \log^2(x), \quad (x\geq 2).
\end{align}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[german]{authblk}
\usepackage[format=plain,labelfont={bf}]{caption}
\usepackage{listings}
\usepackage[shortcuts]{extdash} % \-/
\usepackage{xcolor}
\usepackage{widetext}
\usepackage{hyperref}

@@

We will define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$
as the real part of its complex continuation.  The real dilogarithm
can be mapped onto the interval $[0,1/2]$ by using the following
identities:
%
\begin{widetext}
\begin{align}
  \Li(x) &= -\Li\left(\frac{1}{1-x}\right) - \frac{\pi^2}{6} + \log(1-x)\left[\frac{1}{2}\log(1-x) - \log(-x)\right], \quad (x<-1), \\
  \Li(x) &= -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\log^2(x), \quad (-1<x<0), \\
  \Li(x) &= -\Li(1-x) + \frac{\pi^2}{6} - \log(x) \log(1-x), \quad (\frac{1}{2}\leq x<1), \\
  \Li(x) &= \Li\left(1-\frac{1}{x}\right) + \frac{\pi^2}{6} - \log(x)\left[\log\left(1-\frac{1}{x}\right) + \frac{1}{2}\log(x)\right], \quad (1<x<2), \\
  \Li(x) &= -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \log^2(x), \quad (x\geq 2).
\end{align}
\end{widetext}
